---
title: "ProjectOne"
output: html_document
---


# Data Project One

## 100 points
# DUE Oct 8 at Midnight

Below are the questions for the first data practical assignment. This project uses the "FossilAnts.csv" file, located in the data directory for the project. The point value of each question is denoted next to it. A blank cell is below each for your answer; feel free to create more blank cells as needed.

0. (5 pts) Create a directory called `projects`, and in it, a subdirectory called `project_one`. Use `download.files` to get [this file](https://github.com/BiologicalDataAnalysis2019/2021/blob/master/projects/project_one/ProjectOne.Rmd), and [this one](https://github.com/BiologicalDataAnalysis2019/2021/blob/master/projects/project_one/data/FossilAnts.csv).



1. 5 pts. Import the `tidyverse` package and load the data. The data for this part of the practical is located in the data directory. Save the data in a variable called `project_dat`. Print the data to the screen to ensure it loaded correctly.

```{r}
project_dat <- read_csv("/cloud/project/projects/FossilAnts.csv")
View(project_dat)
```

2. (5pts) Check the datatypes of each column. There is a column called reference number. This is a static identifier - it should not be changed, and is an indexer used to identify this specimen uniquely. Do we want to treat it as an integer (this is an opinion question - answers may vary).

```
# yes
```

3. (5 pts) Change the datatype of the reference number column to character. Take a peek at the function as.character().

```{r}
 as.character(project_dat$reference_no)

```

4. (5 pts) Look at your data. What are the missing data values? In particular, have a look at the `Tribe` column. In your opinion, are these intelligent missing values for the dataset? Why or why not? If not, how would you like to change them? 

```
They are and I would change the none to NA 

#AMW: If they're intelligent, why change them? 

```

6. (5 points) Are there any columns in your dataset that contain two pieces of data? If so, identify them.

```
# Taxon
```

7. (5pts) Please look at the help page for the `separate` function.

```{r}
?separate()
```


7. (10 pts) How could you separate one column into two? 

```{r}
project_dat <- separate(project_dat,taxon, into = c("genus", "species"), sep = "_")
```

Next, we will test a hypothesis. Your hypthesis is that there are more specimens in the 75 million years ago (mya) - 100 mya interval than the 30 mya to the present interval.

8. (5 pts) Write out the steps you would take to address this question. Will you need to split up the data? Will you need to group the data based on the values in some column? 

# I would check too see the amount of samples we have in the 75mya and up in the minimum age and maximum age and the same for 30 mya. Then compare the amounts with each other to see which one has more samples in it


9. (15 pts) Perform the operations you described in (8). 

```{r}
 project_dat$min_ma[project_dat$min_ma > 75.000]
 project_dat$min_ma[project_dat$min_ma < 30.000]

```

10. (5 pts) Do the results of your code support the hypothesis? 

```
# No it showed that there are more samples in the 30 mya to present interval than 75 - 100 mya interval.

#AMW: How did you assess this? Seems hard to do visually? 
```


11. (10 pts) Save the dataframe with the split columns into a new directory called `project_one_data_output`. Save it as a csv file called "column_separated.csv" 

```{r}
write_csv(project_dat, path = "/cloud/project/projects/projects_one/project_one_data_output/column_separated.csv")
       

```

12. (10 pts) Produce a histogram of the number of specimens by minimum age. Look at the geom_histogram() help.

```{r}
ggplot(data = ProjectNA, mapping = aes(x = min_ma)) + geom_histogram()

```

13. (5 pts) Change the font size on your histogram so that it can be read comfortably on your computer screen from five feet away. Save the file as "large_font.pdf".

```{r}
 ggplot(data = ProjectNA, mapping = aes(x = min_ma)) + geom_histogram() +
 theme(text = element_text(size = 16))
```

14. Finally, produce a histogram of counts for each subfamily.

```{r}
ggplot(data = Projectcount, mapping = aes(x = n, fill = subfamily)) + geom_histogram()

```
For the graduate section I choose to seperate the columns from the ones with zero. The other two I decided to make a histogram of the diffrences and then alter the size of the information. I belive that doing those steps can help clean out columns and make good graphs to show the information.
data summary states generaled from revbayes morphological data
1.

```{r}
library(dplyr)
NoZero <- MyData %>%
summarize(`Theta`, `Tajima-D`, `Tajima-Pi`, `Segregating-Sites`, `Max Pairwise Difference`, `Max Pairwise Difference Excluding Ambiguous`, `Max Variable Block Length`, `Max Variable Block Length Excluding Ambiguous`, `Min Pairwise Difference`, `Min Pairwise Difference Excluding Ambiguous`)
```

2. 

```{r}
ggplot(data = MyData, mapping = aes(x = `Max Pairwise Difference`)) + geom_histogram()

```
3. 
```{r}
ggplot(data = MyData, mapping = aes(x = `Max Pairwise Difference`)) + geom_histogram() + theme(text = element_text(size = 16))
```